Adopting agile in the large: motivations, success factors and challenges

### 2014-01-14 journal/article.tex
Better explanation on preliminary searches

Before proceeding with the keyword search a series of preliminary searches were
performed. Initial searches were made using keywords that were as general as
possible, including ``agile transformation'' and ``large scale agile''.
Additionally, a keyword search was done in the selected databases (listed in
table \ref{table:databases}) using the following search string:

@@

From these searches we compiled a list of 117 possibly relevant papers that
should be matched by the keyword searches. The keyword search came to include 75
of the preliminarily selected papers. The missed 32 preliminary papers were
separately examined for inclusion, resulting in including 3 additional papers as
primary studies.
% -->  Move this later.

@@

@@

Full text filtering was performed by evaluating each article against the three
facets of the inclusion criteria. Filtering was done in two steps. In the first
step Dikert extracted data relevant to the three facets of the inclusion
criteria. Based on the extracted data 76 papers could be immediately deemed as
included or excluded. The remaining 94 papers were evaluated against the
inclusion criteria by both Dikert and Paasivaara, and a decision was made after
discussing each paper separately. In difficult cases Lassenius was consulted to
reach a decision. As a result of the full text filtering 45 papers were selected
to be included.
In addition 2 papers were included from the references of the evaluated papers,
and 3 papers were included from the results of the preliminary search. Finally,
50 papers were selected as primary studies.

>>>>

Before proceeding with the database search a number of preliminary searches were
performed. The purpose of the preliminary searches was to create a benchmark of
potentially relevant papers that should be matched by the actual database
search. We also wanted to list top ranked hits by trivial keywords that the
more complex final search string might miss. Initial searches were made using
keywords that were as general as possible, including ``agile transformation''
and ``large scale agile''. Additionally, a trial keyword search was done in the
selected databases (listed in table \ref{table:databases}) using the following
search string:

@@

From these preliminary searches we compiled a list of 117 possibly relevant
papers that should be matched by the actual database search.

@@

We also evaluated the keyword search against the benchmark created in the
preliminary search step, concluding that 75 of the 117 preliminarily selected
papers matched. The missed 32 preliminary papers were examined, resulting in
including 3 additional papers as primary sources.

@@

Full text filtering was performed by evaluating each article against the three
facets of the inclusion criteria. Filtering was done in two steps. In the first
step Dikert extracted data relevant to the three facets of the inclusion
criteria. Based on the extracted data 76 papers could be immediately deemed as
included or excluded. The remaining 94 papers were evaluated against the
inclusion criteria by both Dikert and Paasivaara, and a decision was made after
discussing each paper separately. In difficult cases Lassenius was consulted to
reach a decision. As a result of the full text filtering 45 papers were selected
to be included.

In the full text filtering step the references of all papers were also examined
for relevance, including 2 referenced papers as primary sources. Most case study
papers used references very scarcely, mostly referencing well known descriptions
of agile methods.

Finally, counting 45 papers from the full text filtering step, 3 papers from
preliminary searches, and 2 papers from references, 50 papers were selected
as primary studies.
